Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-26 paper/paper.tex
Updates from Overleaf

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
\orcid{0002-1601-8729}
\author{Jane Greenberg}
\author{David Breen}
\orcid{0002-1376-5008}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Pepper, Greenberg and Breen}

@@

\section{Discussion}
Text \textit{texty text}%~\cite{Lamport:LaTeX}
\subsection{Future Work}
\section{Conclusion}
Text \textbf{text}

>>>>

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Joel Pepper}
\email{jcp353@drexel.edu}
\orcid{0002-1601-8729}
\author{Jane Greenberg}
\orcid{0001-7819-5360}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}
\author{Yasin Bakis}
\orcid{0001-6144-9440}
\author{Henry Bart Jr.}
\orcid{0002-5662-9444}
\affiliation{
  \institution{Tulane University}
  \city{New Orleans}
  \state{Louisiana}
  \country{USA}
}
\author{David Breen}
\orcid{0002-1376-5008}
\affiliation{%
  \institution{Drexel University}
  \streetaddress{3675 Market St}
  \city{Philadelphia}
  \state{Pennsylvania}
  \country{USA}
  \postcode{19104}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Pepper, Greenberg, Bakis, Bart and Breen}

@@

\section{Discussion}
Text \textit{texty text}%~\cite{Lamport:LaTeX}
\subsection{Future Work}
\begin{itemize}
    \item Further fine tuning of pixel analysis (e.g.\ thresholding on different regions of the bbox)
    \item Generalizing ruler reading
    \item Training on a progressively larger number of image collections to hopefully gain reasonable generality for the whole class of fish specimen images
    \item Adding things like seahorses and eels
    \item Fitting a ``spine'' to specimen
\end{itemize}
\section{Conclusion}
Text \textbf{text}
